{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-26 thesis/thesis.tex
more acks

Looking back on my 11 years at CMU,
I am especially grateful for the early friendships %made early on %in my undergrad years
that continued well past first graduation.
From those who stayed in Pittsburgh %with me
to those who %moved away but % can comment 'moved away but'
kept in touch,
from regular tabletop, board, and/or dance gaming partners
to those who %inexhaustibly
%welcomed me with
offered
company and
a couch to sleep on while I traveled, %during travel,
I thank
%-- and in any order other than alphabetical here would be far too cruel --
8~Gianfortoni,
Adam Blank,
Alan Vangpat,
Alex Yuschik,
Anand Subramanian,
Andrew Krieger,
car bauer,
Carolyn Sawyer,
Elizabeth ``Kempy'' Kemp,
Elly Fong-Jones,
E.~Forney,
Emily~J Leathers,
Emma Cating-Subramanian,
Eric Faust,
Gabriel Mengde Routh,
Greg Hanneman,
hazel vird\'{o},
Jack Ferris,
Jake Lengyel,
Jason ``Wyrm'' Deng,
Joshua Keller,
Joshua Wise,
Josiah Boning,
Julia Tuttle,
Kartik Null Cating-Subramanian,
Kellie ``K2'' Medlin,
Laura Abbott,
Maija E. Mednieks,
Margaret Meyerhofer,
Michael A\texttt{rntz}enius,
Michael ``Sully'' Sullivan,
Miriam Zimmerman,
Naomi Saphra,
Nathaniel Wesley Filardo,
Rhett Lauffenburger,
Richard Ha,
rglenn,
Ryan Pearl,
Todd Eisenberger,
and
Zachary McCord
for their wonderful friendship.
I am equally grateful to the new friends I made during my graduate years,
whether through board/card/dance gaming, tea drinking, %and/or
movie watching,
and/or as more permanent Pittsburgh residents that I am extremely torn up about moving away from:
%leaving behind (for now at least):
Alexandra Lee Falk,
Alexis Dyer,
Barbara Jensen,
Brendan McShane,
Brian Saghy,
Carlo Angiuli,
Cassie Orr,
Charlie McGuffey,
Dan Guzek,
Danny Gratzer,
David Renshaw,
Evan Cavallo,
Gabriele Farina,
Grant Wu,
Isaac Grosof,
jennylin,
Karl Schulz,
Kevin Nguyen,
Kristy Gardner,
Lea Albaugh,
Marlena N. Abraham,
Matt Stanec,
Matthew Maurer,
Priya Donti,
Roie Levin,
Ryan Kavanagh,
Sarah R. Allen,
Sol Boucher,
Sophia Wu,
Stefan Muller,
Zachary Waldman,
Ziv Scully,
and the rest of ThursDz already named previously.
And to anyone who may read this list
and feel even slightly dejected that their name was left out:
I owe you a nice dinner. Get in touch.

>>>>

Looking back on my 11 years at CMU,
I am especially grateful for the early friendships %made early on %in my undergrad years
that continued well past first graduation.
From those who stayed in Pittsburgh %with me
to those who %moved away but % can comment 'moved away but'
kept in touch,
from regular tabletop, board, and/or dance gaming partners
to those who %inexhaustibly
%welcomed me with
offered
company and
a couch to sleep on while I traveled, %during travel,
I thank
%-- and in any order other than alphabetical here would be far too cruel --
8~Gianfortoni,
Adam Blank,
Alan Vangpat,
Alex Yuschik,
Anand Subramanian,
Andrew Krieger,
car bauer,
Carolyn Sawyer,
Elizabeth ``Kempy'' Kemp,
Elly Fong-Jones,
E.~Forney,
Emily~J Leathers,
Emma Cating-Subramanian,
Eric Faust,
Gabriel Mengde Routh,
Greg Hanneman,
hazel vird\'{o},
Jack Ferris,
Jake Lengyel,
Jason ``Wyrm'' Deng,
Joshua Keller,
Joshua Wise,
Josiah Boning,
Julia Tuttle,
Kartik Null Cating-Subramanian,
Kellie ``K2'' Medlin,
Laura Abbott,
Maija E. Mednieks,
Margaret Meyerhofer,
Michael A\texttt{rntz}enius,
Michael ``Sully'' Sullivan,
Miriam Zimmerman,
Naomi Saphra,
Nathaniel Wesley Filardo,
Rhett Lauffenburger,
Richard Ha,
rglenn,
Ryan Pearl,
Todd Eisenberger,
and
Zachary McCord
for their wonderful friendship.
I am equally grateful to the new friends I made during my graduate years,
whether through board/card/dance gaming, tea drinking, %and/or
movie watching,
and/or as more permanent Pittsburgh residents that I am extremely
sad to move away from:
%torn up about moving away from:
%leaving behind (for now at least):
Alexandra Lee Falk,
Alexis Dyer,
Barbara Jensen,
Brendan McShane,
Brian E. Saghy,
Carlo Angiuli,
Cassie Orr,
Charlie McGuffey,
Dan Guzek,
Danny Gratzer,
David Renshaw,
Evan Cavallo,
Gabriele Farina,
Grant Wu,
Isaac Grosof,
jennylin,
Karl Schulz,
Kevin Nguyen,
Kristy Gardner,
Lea Albaugh,
Marlena N. Abraham,
Matt Stanec,
Matthew Maurer,
Priya Donti,
Roie Levin,
Ryan Kavanagh,
Sarah R. Allen,
Sol Boucher,
Sophia Wu,
Stefan Muller,
Zachary Waldman,
Ziv Scully,
and the rest of ThursDz already named previously.
And to anyone who may read this list
and feel even slightly dejected that their name was left out:
I owe you a nice dinner. Get in touch.
